Semantic Linearity in a Lazy Optimising Compiler

### 2024-02-12 icfp.tex
removed todo on case-let

\subsection{Optimisations preserve linearity\label{sec:optimisations-preserve-types-meta}}
\todo[inline]{Check Commuting case-let in Fig.~\ref{fig:opttrans}!}
A main goal of the Linear Core type system is 
to serve as a typed intermediate representation for optimising
compilers of lazy languages with linearity. In light of this,
we show that multiple optimising transformations are type
preserving in Linear Core (i.e.,~preserve linearity semantically).

>>>>

\subsection{Optimisations preserve linearity\label{sec:optimisations-preserve-types-meta}}
%\todo[inline]{Check Commuting case-let in Fig.~\ref{fig:opttrans}!}
A main goal of the Linear Core type system is 
to serve as a typed intermediate representation for optimising
compilers of lazy languages with linearity. In light of this,
we show that multiple optimising transformations are type
preserving in Linear Core (i.e.,~preserve linearity semantically).
